|

### 2021-05-30 appendix/appendix.Rmd
unicameralism added to meta-regressions

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='logExpPC',
              slab = fulldat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

@@

2. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
summary(mod)
```

@@

3. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.

@@

6. The institutional design: whether the legislature in the analysis is unicameral, bicameral, or mixed.

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = dat$authoryear)

summary(mod)
```
In the restricted model, with only the main coefficients in the selected papers, only Unicameralism has a positive, significant effect. We also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = fulldat$authoryear)
summary(mod)
```
In the full model, we can see that:

1. Coefficients from non-majoritarian systems are significantly lower than those found in purely majoritarian systems.

2. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.

3. Evidence from unicameral systems presents significantly larger effect sizes.

4. All other moderators are insignificant.

>>>>

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = fulldat$depvar2=='logExpPC',
              slab = fulldat$authoryear)

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              subset = dat$depvar2=='PCTGDP',
              slab = dat$authoryear)

@@

2. Papers whose samples included unicameral legislatures report slightly higher coefficients.

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
summary(mod)
```

@@

3. Papers whose samples included unicameral legislatures report significantly higher coefficients.

@@

6. The institutional design: whether the legislature in the analysis is unicameral or non-unicameral (bicameral or mixed).

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = dat$authoryear)

summary(mod)
```
In the restricted model, with only the main coefficients in the selected papers, Unicameralism has a positive, significant effect. Also, papers using Regression Discontinuity Design tend to have a negative effect, significant at the 10% level. We also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
              test = "knha",
              tdist = TRUE,
              sparse = TRUE,
              slab = fulldat$authoryear)
summary(mod)
```
In the full model, we can see that:

1. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.

2. Evidence from unicameral systems presents significantly larger effect sizes.

3. All other moderators are insignificant.
